---
title: "HRI_Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)

# set working directory
setwd("/home/hannah/Documents/A0_uni/S5/HRI/Data/")
```

```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
# load the data
data <-list.files(pattern = "*.csv") %>%
  map_df(~read_csv(.))

post_questionnaire <- read.csv("../Post-Questionnaire.csv")
```


```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# preprocessing
# clean up ids
data$participantID[data$participantID == 3225] <- 2
data$participantID[data$participantID == 123098] <- 3
data$participantID[data$participantID == 89345] <- 0

# add choice numbers to trials
data <- data %>% group_by(participantID, trialNumber) %>% mutate(choice_nb = row_number()-1) %>% ungroup()

# exclude participant 6

# avatar LoM is ordered
data$levelOfMatchChosen <- factor(data$levelOfMatchChosen, levels=c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch"), ordered=TRUE)
data$levelOfMatchOther <- factor(data$levelOfMatchOther, levels=c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch"), ordered=TRUE)
data$participantID <- factor(data$participantID)

# cleaning up column names
names(post_questionnaire) <- c("time", "participantID", "video_games", "avatar_appearance", "selection_based_on", "selection_reason", "clothing style", "clothing color", "hairstyle", "hair color", "remarks")
# likert scales are factors
post_questionnaire$video_games <- factor(post_questionnaire$video_games, levels=c("never", "sometimes", "often"), ordered = TRUE)
post_questionnaire$avatar_appearance <- factor(post_questionnaire$avatar_appearance, levels=c("1", "2", "3", "4", "5"), ordered = TRUE)
post_questionnaire$selection_based_on <- factor(post_questionnaire$selection_based_on, levels=c("random", "a \"gut feeling\" (\"Bauchgefühl\")", "with reasoning"))
# post_questionnaire$clothing_style <- factor(post_questionnaire$clothing_style, levels=c("1", "2", "3", "4", "5"), ordered = TRUE)
# post_questionnaire$clothing_color <- factor(post_questionnaire$clothing_color, levels=c("1", "2", "3", "4", "5"), ordered = TRUE)
# post_questionnaire$hairstyle <- factor(post_questionnaire$hairstyle, levels=c("1", "2", "3", "4", "5"), ordered = TRUE)
# post_questionnaire$hair_color <- factor(post_questionnaire$hair_color, levels=c("1", "2", "3", "4", "5"), ordered = TRUE)

post_questionnaire <- post_questionnaire %>% select(-time)
```

## Post questionnaire
```{r echo=FALSE, warning=FALSE, message=FALSE}
p_data <- post_questionnaire

# rating of the avatar appearance
p_data %>%
  ggplot()+
  geom_bar(aes(avatar_appearance, fill=avatar_appearance))+
  theme_light(base_size=40)+
  xlab("Appearance rating")+
  theme(legend.position = "none")+ 
  scale_fill_discrete(drop=FALSE) +
  scale_x_discrete(drop=FALSE)

ggsave("AppearanceRating.png", width = 50, height = 30, units = "cm")

# choice based on
p_data %>%
  ggplot()+
  geom_bar(aes(selection_based_on, fill=selection_based_on))+
  theme_light(base_size=40)+
  xlab("Avatar selection was")+
  theme(legend.position = "none")+ 
          scale_fill_discrete(drop=FALSE) +
          scale_x_discrete(drop=FALSE)

ggsave("SelectionBasedOn.png", width = 50, height = 30, units = "cm")


p_data <- p_data %>% select(c(participantID, `clothing style`, `clothing color`, hairstyle, `hair color`)) %>%
  pivot_longer(cols = -1, names_to = "type", values_to = "rating")

p_data %>%
  ggplot(aes(rating, type, fill = type))+
  geom_boxplot()+
  theme_light()+
  xlab("Influence on Avatar Pick")+
  ylab("Type")+
  theme(legend.position = "none")

p_data %>% filter(participantID != 6) %>%
  ggplot(aes(rating, type, fill = type))+
  geom_boxplot(lwd=2)+
  theme_light(base_size=40)+
  xlab("Influence on Avatar Pick")+
  ylab("")+
  theme(legend.position = "none",
        axis.text.y = element_text(c("hairstyle", "hair color", "clothing style", "clothing color")))

ggsave("InfluenceOnAvatarSelection.png", width = 50, height = 30, units = "cm")

```

# Colors - participants choices and mean
## Skin color
```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE}
skin_colors <- data[c("participantID", "SkinColor_r", "SkinColor_g", "SkinColor_b")]

skin_colors <- skin_colors %>% rename(r=SkinColor_r, g=SkinColor_g, b=SkinColor_b) %>% group_by(skin_colors$participantID) %>% unique()
pal <- rgb(skin_colors$r, skin_colors$g, skin_colors$b)
plot <- show_col(pal, labels=TRUE, borders = NA)
print(plot)
# mean color
s <- colMeans(skin_colors)
print(s)

pal <- rgb(s["r"], s["g"], s["b"])
show_col(pal)

```

## Hair color
```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# naming is wrong, actually eye color
hair_colors <- data[c("participantID", "HairColor_r", "HairColor_g", "HairColor_b")]

hair_colors <- hair_colors %>% rename(r=HairColor_r, g=HairColor_g, b=HairColor_b) %>% group_by(hair_colors$participantID) %>% unique()

pal <- rgb(hair_colors$r, hair_colors$g, hair_colors$b)
show_col(pal, labels=TRUE, borders = NA)

# mean
s <- colMeans(hair_colors)
print(s)

pal <- rgb(s["r"], s["g"], s["b"])
show_col(pal)

```

## Eye color
```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# naming is wrong, actually hair color
eye_colors <- data[c("participantID", "EyeColor_r", "EyeColor_g", "EyeColor_b")]

eye_colors <- eye_colors %>% rename(r=EyeColor_r, g=EyeColor_g, b=EyeColor_b) %>% group_by(eye_colors$participantID) %>% unique()

pal <- rgb(eye_colors$r, eye_colors$g, eye_colors$b)
show_col(pal, labels=TRUE, borders = NA)

#show mean
s <- colMeans(eye_colors)
print(s)

pal <- rgb(s["r"], s["g"], s["b"])
show_col(pal)

```

## Favourite color
```{r echo = FALSE, echo=FALSE, warning=FALSE, message=FALSE}
favourite_colors <- data[c("participantID", "FavouriteColor_r", "FavouriteColor_g", "FavouriteColor_b")]

favourite_colors <- favourite_colors %>% rename(r=FavouriteColor_r, g=FavouriteColor_g, b=FavouriteColor_b) %>% group_by(favourite_colors$participantID) %>% unique()

pal <- rgb(favourite_colors$r, favourite_colors$g, favourite_colors$b)
show_col(pal, labels=TRUE, borders = NA)

#show mean
s <- colMeans(favourite_colors)
print(s)

pal <- rgb(s["r"], s["g"], s["b"])
show_col(pal)
```
-> 3 participants selected their favourite color twice, participant 1 had to restart and 2 and 6 changed after trial 0. All clearly tried to select the same color again.

# Overview of other preferences - Hair style, clothing style, likes glasses, likes hats
```{r echo=FALSE, warning=FALSE, message=FALSE}
data <- data %>% ungroup()
h <- data %>% select(participantID, HairLength) %>% group_by(participantID) %>% unique()
h %>%
  ggplot+
  geom_bar(aes(x=HairLength))+
  xlab("Hair style")+
  theme_light()

h <- data %>% select(participantID, ClothingStyle) %>% group_by(participantID) %>% unique()
h %>%
  ggplot+
  geom_bar(aes(x=ClothingStyle))+
  xlab("Clothing style")+
  theme_light()

h <- data %>% select(participantID, LikesGlasses) %>% group_by(participantID) %>% unique()
h %>%
  ggplot+
  geom_bar(aes(x=LikesGlasses))+
  xlab("Likes glasses")+
  theme_light()

h <- data %>% select(participantID, LikesHats) %>% group_by(participantID) %>% unique()
h %>%
  ggplot+
  geom_bar(aes(x=LikesHats))+
  xlab("Likes hats")+
  theme_light()

#+ theme(text = element_text(size = 24))
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
f <- data %>% select(participantID, trialNumber, levelOfMatchChosen:choice_nb) %>% filter(participantID!=6)
sum(f$levelOfMatchChosen > f$levelOfMatchOther)/length(f$levelOfMatchChosen)

f <- f %>% mutate(chosenBetter = f$levelOfMatchChosen > f$levelOfMatchOther)



# plot the ratios for the individual participants
ratios <- f %>% group_by(participantID)%>% 
  summarise(n=n(), choiceRatio = sum(chosenBetter)/n)

ratios%>%
  ggplot()+
  geom_bar(aes(y=choiceRatio, x=participantID, fill=participantID),
                    position = "dodge",
                    stat = "identity")+
  theme_light(base_size=40)+
  xlab("Participant ID")+
  ylab("Probability of Selecting Higher LoM Avatar")+
  theme(legend.position = "none")


ggsave("ChoiceRatios.png", width = 50, height = 30, units = "cm")

ratios <- f %>% group_by(participantID)%>% 
  summarise(n=n(), choiceRatio = mean(chosenBetter))
mean(ratios$choiceRatio)
min(ratios$choiceRatio)
max(ratios$choiceRatio)


```

# Thinking time vs kept avatar
```{r echo=FALSE, warning=FALSE, message=FALSE}
d <- data %>% select("participantID", "ThinkingTime", "keptSameAvatar")
d <- d %>% filter(ThinkingTime <= 40)

s <- d %>% group_by(keptSameAvatar) %>% summarize(mean=mean(ThinkingTime), sd = sd(ThinkingTime))
x <- d %>% filter(keptSameAvatar==FALSE)
y <- d %>% filter(keptSameAvatar==TRUE)
x %>% summarize(mean=mean(ThinkingTime), sd = sd(ThinkingTime))
y %>% summarize(mean=mean(ThinkingTime), sd = sd(ThinkingTime))
# paired t-test
#d
#r <- d %>% ungroup() %>% t.test(ThinkingTime ~ keptSameAvatar, var.equal = FALSE)
t.test(x, y, alternative="greater", var.equal = FALSE)
d %>%
  ggplot(aes(x=keptSameAvatar, y=ThinkingTime, color=keptSameAvatar))+
  geom_boxplot(lwd=2)+
  geom_violin(fill="transparent", outline.type = "both")+
  geom_point(position=position_jitter(h=0, w=0.3))+
  theme_light(base_size=40)+
  xlab("Kept the Avatar")+
  ylab("Thinking Time")+
  theme(legend.position = "none")
  
  


ggsave("ThinkinTimeVsKeptAvatar.png", width = 50, height = 30, units = "cm")

  
```



