---
title: "Avatar the Legend of VR Analysis"
output: html_document
---


```{r, include = F}
library("purrr")
library("readr")
library("tidyverse")
library("dplyr")
library("ggplot2")
setwd("D:/NoOneDrive/DataScience/Tools/CSV Tools/")
```

```{r, include = F}
data <- read.csv("NewCSV.csv")
```
```{r}
summary(data)
```


```{r}
wo_prefs <- data %>%
  select(participantID, trialNumber, ChoiceNo, levelOfMatchChosen, levelOfMatchOther, ThinkingTime, TimeLookedAtMatch, TimeLookedAtOther, keptSameAvatar) %>%
  filter(levelOfMatchOther != levelOfMatchChosen)
wo_prefs$levelOfMatchOther <- factor(
  wo_prefs$levelOfMatchOther, ordered = T,
  levels = c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch"))
wo_prefs$levelOfMatchChosen <- factor(
  wo_prefs$levelOfMatchChosen, ordered = T,
  levels = c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch"))
wo_prefs$keptSameAvatar <- as.logical(wo_prefs$keptSameAvatar)

wo_prefs <- wo_prefs %>%
  filter(trialNumber != 5 & participantID != 6) %>%
  mutate(
    choiceIdx = trialNumber * 4 + ChoiceNo,
    chosen_num = case_when(
      levelOfMatchChosen == "FullMatch" ~ 5,
      levelOfMatchChosen == "BetterMatch" ~ 4,
      levelOfMatchChosen == "SlightMatch" ~ 3,
      levelOfMatchChosen == "LessOpposite" ~ 2,
      levelOfMatchChosen == "Opposite" ~ 1,
    ),
    other_num = case_when(
      levelOfMatchOther == "FullMatch" ~ 5,
      levelOfMatchOther == "BetterMatch" ~ 4,
      levelOfMatchOther == "SlightMatch" ~ 3,
      levelOfMatchOther == "LessOpposite" ~ 2,
      levelOfMatchOther == "Opposite" ~ 1,
    ),
    distance = as.factor(abs(chosen_num - other_num)),
    combination = chosen_num + other_num
  )

```
```{r}
summary(wo_prefs)
```
## Did response time got faster the more choices they faced?
```{r}
wo_prefs %>% nrow %>% cat("before\n")
time_data <- wo_prefs %>%
  filter(ThinkingTime < 40)
time_data %>% nrow %>% cat("after\n")

cat("Correlation between overall choice number and thinking time:", with(time_data, cor(choiceIdx, ThinkingTime)))
time_data %>%
        ggplot(aes(choiceIdx, ThinkingTime)) + geom_jitter(size=4, width = .4) +
  geom_smooth() + ylab("Thinking time") + xlab("Choice number") +
  theme_light() + theme(text = element_text(size = 24))
```

```{r}
summary(time_data)
```

# Did the response time go down when they kept their character in the following decision?
```{r}
time_data %>%
  ggplot(aes(keptSameAvatar, ThinkingTime, color = keptSameAvatar)) + geom_boxplot() + geom_jitter(width = .2) + theme_light() + guides(color = "none") +
  ylab("Thinking time") + xlab("Kept the avatar?") + theme(text = element_text(size = 24))
```

# Were response times faster when character was closer to their liking?
```{r}
time_data %>%
  ggplot(aes(levelOfMatchChosen, ThinkingTime)) + geom_boxplot() + geom_jitter(width = .2) + theme(text = element_text(size = 24))
```

```{r}
time_data %>%
  ggplot(aes(levelOfMatchChosen, TimeLookedAtOther, color = keptSameAvatar)) + geom_boxplot() + geom_jitter(width = .2) +
  ylim(0, 5) + xlab("LoM Chosen Avatar") + ylab("Time looked at rejected avatar") + labs(color = "Kept the same avatar?") + theme_light() + theme(text = element_text(size = 20))
```

## Which combinations of choices were present?
```{r}
wo_prefs %>%
  mutate(
    A = case_when(
      levelOfMatchChosen < levelOfMatchOther ~ levelOfMatchChosen,
      TRUE ~ levelOfMatchOther
    ),
    B = case_when(
      levelOfMatchChosen > levelOfMatchOther ~ levelOfMatchChosen,
      TRUE ~ levelOfMatchOther
    )
  ) %>%
  ggplot(aes(A, B)) + geom_count() + ylab("") + xlab("") + theme_light() + theme(text = element_text(size = 26))
```
## How often which level was chosen
```{r}
wo_prefs %>%
  ggplot(aes(levelOfMatchChosen, fill=levelOfMatchChosen)) +
  geom_bar() + labs(fill="LoM Chosen Avatar") + xlab("LoM Chosen Avatar") +
  theme_light() + theme(text = element_text(size = 24))
```

# How often each level was chosen per trial
```{r}
wo_prefs %>% mutate(trail=as.factor(trialNumber + 1)) %>%  ggplot(aes(trail, fill=levelOfMatchChosen)) + geom_bar()+ labs(fill="LoM Chosen Avatar") + xlab("Trial number") +
  theme_light() + theme(text = element_text(size = 24))
```

# The probability of choosing a specific LoM
```{r}
perc_chosen <- function(value){
  nrow(filter(wo_prefs, levelOfMatchChosen == value))/ nrow(filter(wo_prefs, levelOfMatchChosen == value | levelOfMatchOther == value))
}

values <- c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch")

x <- data.frame(
    LoM=values,
    Perc=c(perc_chosen("Opposite"),
            perc_chosen("LessOpposite"),
            perc_chosen("SlightMatch"),
            perc_chosen("BetterMatch"),
            perc_chosen("FullMatch"))
)

x$LoM <- factor(x$LoM, ordered = T, levels = values)

x %>% ggplot(aes(x=LoM, y=Perc, fill=LoM)) +
  geom_bar(stat = 'identity') +
  scale_y_continuous(n.breaks=9, limits = c(0, 0.8)) +
  theme_light() +
  xlab("LoM Chosen Avatar") +
  ylab("Selection Probability") +
  labs(fill="LoM Match Avatar") +
  theme(text = element_text(size = 24))
```

# Probability of keeping an Avatar
```{r}
perc_kept <- function(value){
  wo_prefs %>% filter(levelOfMatchChosen == value & keptSameAvatar) %>% nrow /
    wo_prefs %>% filter(
      (levelOfMatchChosen == value | levelOfMatchOther == value) & ChoiceNo != 1
    ) %>% nrow
}

values <- c("Opposite", "LessOpposite", "SlightMatch", "BetterMatch", "FullMatch")

x <- data.frame(
  LoM=values,
  Perc=c(perc_kept("Opposite"),
         perc_kept("LessOpposite"),
         perc_kept("SlightMatch"),
         perc_kept("BetterMatch"),
         perc_kept("FullMatch"))
)

x$LoM <- factor(x$LoM, ordered = T, levels = values)

x %>% ggplot(aes(x=LoM, y=Perc, fill=LoM)) +
  geom_bar(stat = 'identity') +
  scale_y_continuous(n.breaks=7, limits = c(0, 0.6)) +
  theme_light() +
  xlab("LoM Chosen Avatar") +
  ylab("Probability of Keeping") +
  labs(fill="LoM Match Avatar") +
  theme(text = element_text(size = 24))
```

# How often the avatar was kept
```{r}
wo_prefs %>%
  filter(keptSameAvatar) %>%
  ggplot(aes(levelOfMatchChosen, fill = levelOfMatchChosen)) +
  geom_bar() +
  theme_light() +
  xlab("LoM Chosen Avatar") +
  labs(fill="LoM Match Avatar") +
  theme(text = element_text(size = 24))
```
